\documentclass[10pt,a4paper,ragged2e]{altacv}
\geometry{left=2cm,right=10cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm}
\ifxetexorluatex
  \setmainfont{Carlito}
\else
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[default]{lato}
\fi
\definecolor{VividPurple}{HTML}{000000}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{2E2E2E}
\colorlet{heading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}
\addbibresource{sample.bib}
\usepackage{hyperref}

\hypersetup{
  colorlinks=true,
  linkcolor=blue!50!red,
  urlcolor=gray!70!black
}

\begin{document}
\name{SHUBHAM DWIVEDI}
\tagline{Fullstack Developer}
% Cropped to square from https://en.wikipedia.org/wiki/Marissa_Mayer#/media/File:Marissa_Mayer_May_2014_(cropped).jpg, CC-BY 2.0
% \photo{3.3cm}{profile.jpg}
\personalinfo{%
  % Not all of these are required!
  % You can add your own with \printinfo{symbol}{detail}
  \email{shubham00d@gmail.com}
  \phone{+919599428859}
%  \mailaddress{Address, Street, 00000 County}
  \location{New Delhi - India}
%  \homepage{marissamayr.tumblr.com/}
%  \twitter{@marissamayer}
  % \linkedin{https://www.linkedin.com/in/shubhamdwivedi27/}
  \linkedin{shubhamdwivedi27}
  \github{shubhamdwivedii}
%   \orcid{orcid.org/0000-0000-0000-0000} % Obviously making this up too. If you want to use this field (and also other academicons symbols), add "academicons" option to \documentclass{altacv}
}

%% Make the header extend all the way to the right, if you want.
\begin{fullwidth}
\makecvheader
\end{fullwidth}

%% Depending on your tastes, you may want to make fonts of itemize environments slightly smaller
\AtBeginEnvironment{itemize}{\small}

%% Provide the file name containing the sidebar contents as an optional parameter to \cvsection.
%% You can always just use \marginpar{...} if you do
%% not need to align the top of the contents to any
%% \cvsection title in the "main" bar.
\cvsection[page1sidebar]{Experience}

\cvevent{Fullstack Developer}{Codalien Technologies Pvt. Ltd.}{Feb 2019 -- Present}{New Delhi, DL, India}
\begin{itemize}
\item Developed both frontend (web and mobile) applications as well as backend services powered by latest web technologies and frameworks.
\smallskip
\item Planned, wrote and debugged the structure and components for the projects, making sure they are reusable.
\smallskip
\item Directly interacted with various client's teams, providing feedback, clarifying requirements and helping with technical questions.
\smallskip
\item Kept the Project Manager and the IT Leads updated on the overall progress of the projects and managed time-sensitive updates, including content changes and database upgrades.
\smallskip
\item Kept the code and the features implemented by the team in accordance to the requirements.
\end{itemize}

\divider

\cvevent{Software Development Intern}{DataGrokr Analytics Pvt. Ltd.}{Jun 2017 - Dec 2017}{Bengaluru, KA, India}
\begin{itemize}
\item Worked independently as well as assisted senior developers in various coding and testing functions. 
\smallskip
\item Worked on several DevOps technologies including AWS Cloud Services (EC2, S3, Route 53,
CloudFormation, API Gateway, etc.), Python, Shell scripting and Chef. 
\smallskip
\item Also built web applications using Angular 2 with back-end REST API powered by python scripts running in
AWS lambda service.
\end{itemize}

%\divider

\cvsection{Projects}

\cvproject{1UPVision VMS - https://www.1upvision.com/} 
\begin{itemize}
\item A visitor management system application with a visitor facing app (VMS) and an admin dashboard app (workspace/visitor management).
\item I contributed to both frontend applications (powered by ReactJS). Ant Design was heavely used for UI elements. 
\item A major contribution was a dynamic form generator where use can drag drop form elements from a toolbar and arrange them to create custom forms (for visitors).
\end{itemize}
\smallskip
\smallskip 


\cvproject{Drata (Electron App) - https://drata.com/}
\begin{itemize}
\item A system monitoring app (Windows, Mac and Linux) designed for employee workstations.
\item After registration, the app runs in background (minimized to system tray) and monitors the system (sending logs to the server).
\item I led the frontend app development using a VueJS frontend running on ElectronJS platform (with Osquery binary files packaged for running system info queries).
\end{itemize}
\smallskip
\smallskip

\cvsection[page2sidebar]{Projects Continued}

\cvproject{Perspectico AI - https://www.perspectico.com/} 
\begin{itemize}
  \item Perspectico is a collection of Job management tools such as AI powered assessment tools, Job search, Competency Tests, Webinars and Courses.
  \item I contributed to the frontend web portal powered by ReactJS during a 3 month overhaul sprint. 
\end{itemize}
\smallskip
\smallskip 

\cvproject{TravX - http://travx.in/} 
\begin{itemize}
\item An application designed for travel agents where they can create/sell travel vouchers and manage their sales and expenses. 
\item A worked as lead developer on both frontend mobile application (VueJS Cordova) and the backend services (KeystoneJS GraphQL).
\item The DB design for this application was a very interesting challenge as it required support for custom travel vouchers which could have a varying number of offers, each offer having multiple subitems with custom info fields.
\item \href{https://play.google.com/store/apps/details?id=com.travx.app}{Playstore Link}
\end{itemize}
\smallskip
\smallskip 


\cvproject{Proximity.io - https://prox.io/} 
\begin{itemize}
\item An application where users can book a one on one sessions with mentors and connect with them via video chat.
\item I worked as a lead developer in first phase of the application (around 6 months) where I contributed to both the frontend web (React), mobile (React-Native) and the backend (Node Express Firestore).
\item The video chat was based on Twilio SDK, Stripe was used for payment gateway, Auth0 for providing social login. 
\item Both the Node/Express app and the React web was deployed on Firebase (Express app as a Firebase Function). Firestore was used as DB. 
\item MobX was used for store management in both web and mobile React apps. Google APIs for providing calendar integration.
\end{itemize}
\smallskip
\smallskip 



\cvproject{Evermee (Mobile App) - https://evermee.com/}
\begin{itemize}
\item An online jewellery store (powered by shopify) that sells jewellery with embedded NFC tags.
\item Users can scan these jewellery in Evermee mobile app, and add a memory (a photograph with text message).
\item I worked on both the fulfillment and user application (with NFC scanning functionality) powered by React-Native (for both iOS and Android). 
\item I also contributed to the backend CMS powered by KeystoneJS (A Node, Mongo based framework that provides a CMS admin panel powered by NextJS).
\item \href{https://play.google.com/store/apps/details?id=com.evermee}{Playstore link}
\end{itemize}
\smallskip
\smallskip


\cvproject{Credbo - https://www.credbo.com/} 
\begin{itemize}
\item An expense management application for retailers and small buisnesses.
\item I contributed to both the mobile application (React-Native) and the backend service (Node MongoDb GraphQl) 
\end{itemize}
\smallskip
\smallskip 


\cvproject{ToyFull (On Going) - https://toyfull-app.web.app/} 
\begin{itemize}
\item An ecommerce web and mobile application targeting kid's toys and apparels. 
\item I am currently working on the both the web (React) and mobile (React Cordova) applications, performing tasks such as fixing/refactoring code, improving data flow, adding/finishing features. 
\item The backend is based on Magento (with additional plugins). 
\end{itemize}
\smallskip
\smallskip 


\cvsection[page3sidebar]{Projects Continued}


\cvproject{LeapSkills - https://www.leapskills.in/} 
\begin{itemize}
\item An educational app where students have access to various study resources, lessons and videos. 
\item I worked on a later stage of the mobile application and improved and added various features such as support for embedded YouTube videos, audio player, pdf viewer and various other components. 
\item Application was based on React-Native. 
\item \href{https://play.google.com/store/apps/details?id=com.leap.skills}{Playstore link}
\end{itemize}
\smallskip
\smallskip 


\cvproject{Novartis PSP - https://www.novartis.com/} 
\begin{itemize}
\item An application for purchasing novartis drugs (for Singapore users only). 
\item I contributed to both the mobile application (React-Native), the web admin interface (React), and the backend server (Node, MySQL, REST)
\item I worked at a later stage of development and performed tasks such as bug fixing, adding new features (such as a free dose claiming flow, push notifications etc.), and code improvements. 
\item \href{https://play.google.com/store/apps/details?id=com.novartispsp}{Playstore link}
\end{itemize}
\smallskip
\smallskip 



\cvproject{MarketMole - https://marketmole.biz/}
\begin{itemize}
\item An Application used by companies such Sony/Netgear to monitor their products sales and reviews on ecommerce websites like amazon, wallmart, etc.
\item I contributed to both the frontend web app (powered by Angular 4) and the backend services (Serverless Node).
\end{itemize}
\smallskip
\smallskip

\cvproject{BMW Prive CRM - https://crm.bmwprive.com}
\begin{itemize}
\item A customer relationship management application for BMW India. 
\item The CRM was based on KeystoneJS v4 with some APIs exposed for BMW Prive website that was developed in ReactJS. 
\item I contributed to both the CRM (by customizing Keystone's default interface according to client's needs) and the Prive website.
\end{itemize}
\smallskip
\smallskip


\cvproject{}

\divider


\clearpage

\nocite{*}

\end{document}
