
\cvsection{Education}
\cvevent{B.Tech. (CSE) - 62.4\%}{Inderprastha Engineering College (AKTU)}{ 2017 }{Ghaziabad, UP}{}
\cvevent{XIIth (CBSE) - 72.5\%}{Tagore Sr. Sec. School}{ 2012 }{Mayapuri, Delhi}{}
\cvevent{Xth (CBSE) - 74.2\%}{N.C. Jindal Public School}{ 2010 }{Punjabi Bagh, Delhi}{}

\cvsection{TECHNICAL SKILLS}
\cvtag{Python}
\cvtag{JavaScript ES6}
\cvtag{ReactJS}
\cvtag{VueJS}
\cvtag{NodeJs}
\cvtag{React Native}
\cvtag{Redux}
\cvtag{MongoDB}
\cvtag{TypeScript}
\cvtag{ExpressJS}
\cvtag{GraphQL}
\cvtag{Amazon Web Services} 
\cvtag{Firebase}
\cvtag{C\#}
\cvtag{Lua}
\cvtag{Linux}
\cvtag{Git}

\cvsection{About}
\smallskip
\begin{itemize}
\item 3 years of experience solving engineering problems.
\smallskip
\item 2+ years of experience writing JavaScript code in production.
\smallskip
\item Deft at reverse engineering / figuring things out with no prior knowledge.
\smallskip
\item Adept at writing testable, modular and simple code.
\smallskip
\item I approach solutions with ”How can it fail” and ”What if it fails” mindset.
\smallskip
\item Skillful in profiling and optimizing code.
\smallskip
\item Really good at finding patterns and relations.
\smallskip
\item Proficient in developing microservices and modules.
\smallskip
\item Experience with MongoDB, Firestore, PostgreSQL.
\smallskip
\item Hands-on experience with AWS technologies such as EC2, S3, Lambda, DynamoDB, CloudFormation.
\smallskip
\item Good grasp on programming fundamentals including OOP, Data Structures and Algorithms.
\end{itemize}
